---
title: Capitalized Title Here
author: Johannes B. Gruber
date: today
format:
  html:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

# Introduction

A few words on what this document accomplishes.
I use one sentence per line to make it easier to see changes with version control, such as on GitHub.

## Packages

Write which packages you use at the beginning so if a package is missing, the script fails early.

```{r}
#| include: false
library("dplyr")
library("ggplot2")
start <- Sys.time() # note start time for later
```

## Data

```{r load data}
data <- ggplot2::diamonds
```

# Main

The main part of the document with analysis and plots.

```{r analysis}
data %>% 
  count(cut)
```

Plot!

```{r plot}
data %>% 
  count(cut) %>% 
  ggplot(aes(x = n, y = cut)) +
  geom_col()
```


# wrap up

Save data if it takes long to preprocess it here. 
Afterwards we get some information which is important to reproduce the report.

```{r}
sessionInfo()
Sys.time()
# note how long the script takes to (re-)run
Sys.time() - start
```
